---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# accmeta

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Meta-analysis of diagnostic accuracy, in terms of sensitivity, specificity and
prevalence. Three estimators are available: a trivariate linear mixed model
(TLMM) using a within-study normal approximation, the trivariate
generalized linear mixed model (TGLMM), and an iterative bootstrap that corrects
the bias of the TLMM by simulating from the TGLMM.

## Example

Setup true parameter value

```{r truepar}
library(accmeta)

th <- c(2.94, -2.2, -0.4, 0.0953, 0.4, -0.5108, 0.3, 0.2, -0.6931)
theta2list(th)
min(eigen(theta2list(th)$SIGMA)$values)

```

Simulate data from true model

```{r data}
set.seed(1)
x <- sim_data(15, th, sample(40:200, 15, TRUE))
head(x)
```

Counts go in through `set_meta_data()`, which checks them and computes the
summaries the models need. 

```{r meta}
d <- set_meta_data(x)
d
```

A continuity correction is needed by the approximate
model whenever a cell is empty. You can use the CC argument:

```{r}
d_cc <- set_meta_data(x, CC = 0.5)
d_cc
```


Now we can fit the models. Note that the TGLMM can be directly fitted on the original data.

```{r fits}
tlmm <- fit_tlmm(d_cc)
tglmm <- fit_tglmm(d)
ib <- fit_ib(d_cc)
ib
```

`coef()` extract estimated parameters:

```{r coef}
coef(tlmm)
coef(tglmm)
coef(ib)

```

All models are estimated, by default, with the recommended Wishart prior. You can change it via

```{r}
tglmm_mle <- fit_tglmm(d, PRIOR = set_prior(DEGREES = 4, SCALE = Inf))
coef(tglmm_mle)
min(eigen(coef(tglmm_mle)$SIGMA)$values)
min(eigen(coef(tglmm)$SIGMA)$values)

```

